Local to global N input modelling

### 2025-06-13 manuscript.qmd
Pre-run big files for speed

```{r raw biomass and weight data}
farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
  list.files(full.names = T)

weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>%
  bind_rows()
biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>%
  bind_rows()
```

@@

fnms <- output_farm_growth_data_path %>% 
  list.files(full.names = T) %>% 
  str_subset("reference")

@@

```{r uneaten feed data}
#| code-summary: Load and prep uneaten feed data

uneaten_total <- farmrun_files %>% 
  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
  bind_rows() %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  rename(uneat_mean = mean.x, biomass_mean = mean.y,
         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
  mutate(uneat_sd = uneat_sd/uneat_mean,
         biomass_sd = biomass_sd/biomass_mean,
         uneat_biom_mean = uneat_mean/biomass_mean,
         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
```

>>>>

```{r raw biomass and weight data}
farmrun_files <- file.path(output_cohorts_data_path) %>% 
  list.files(full.names = T)

weight <- find_read(output_cohorts_data_path, "allfarms_comparisons_weight_stat")
biomass <- find_read(output_cohorts_data_path, "allfarms_comparisons_biomass_stat")
```

@@

fnms <- output_growth_data_path %>% 
  list.files(full.names = T) %>% 
  str_subset("reference")

@@

```{r inputs data}
#| code-summary: Load and prep uneaten feed and faeces data (keep in g faeces/feed)

mass_inputs_ts <- find_read(data_analysis_path, "all_waste_inputs")
mass_inputs_end <- find_read(data_analysis_path, "sumtotal_waste_inputs.qs")
N_inputs_ts <- find_read(data_analysis_path, "all_N_inputs")
N_inputs_end <- find_read(data_analysis_path, "sumtotal_N_inputs")
```
